---
title: "Supp_Figure_Lizards_Arthropods"
author: "CEB"
date: '2024-12-06'
output: html_document
---

#energy flow through arthropods and lizards

#load packages
```{r}
library(tidyverse)

#for bayesian analysis:
library(brms)
library(tidybayes)

#for extracting effects:
library(emmeans)

#for multiple color scales in ggplots:
library(ggnewscale)

#scientific notation funny in some of csvs, fix:
options(scipen=999)

library(cowplot)

```


#load data
```{r}
#arthropod data
arthropod_dat<-read.csv("../data/steibl_tetiaroa_arthropod_energetics_ET.csv")

#lizard data
lizard_dat<-read.csv("../data/steibl_tetiaroa_lizard_energetics_ET.csv")

```

#make adjustments to data based on Sebastian's code:
```{r}

arthropod_dat <- 
  arthropod_dat %>% 
  mutate(across(1:5, as.factor))%>%
  mutate(trap_type = as.factor(trap_type))%>%
  mutate(trap_type = recode_factor(trap_type, "Mal" = "Flying", "Pit" = "Ground-dwelling"))
arthropod_dat


```

###Split arthropods into ground-dwelling and flying, and run flying models-------
```{r}
#hmmm, actually a lot of sites only use one trap or the other. Maybe run 2 seperate models:------
arthropod_dat_fly<-
  arthropod_dat%>%
  filter(trap_type=="Flying")

arthropod_dat_ground<-
  arthropod_dat%>%
  filter(trap_type=="Ground-dwelling")


#should center predictors for modelling (arthropods)------
#create new data:----
range(arthropod_dat_ground$SoilN15, na.rm=TRUE)
range(arthropod_dat_fly$SoilN15, na.rm=TRUE)

arthropod_dat_ground_cs<-
  arthropod_dat_ground%>%
  filter(SoilN15>=0)%>% #easy way to remove NAs because all soil values >= 0
  mutate(native_perc_cs = base::scale(native_perc, center = TRUE, scale = TRUE),
         native_perc_c = base::scale(native_perc, center = TRUE, scale = FALSE),
         soiln15_cs = base::scale(SoilN15, center = TRUE, scale = TRUE),
         soiln15_c = base::scale(SoilN15, center = TRUE, scale = FALSE))

arthropod_dat_fly_cs<-
  arthropod_dat_fly%>%
    filter(SoilN15>=0)%>%#easy way to remove NAs because all soil values >= 0
  mutate(native_perc_cs = base::scale(native_perc, center = TRUE, scale = TRUE),
         native_perc_c = base::scale(native_perc, center = TRUE, scale = FALSE),
         soiln15_cs = base::scale(SoilN15, center = TRUE, scale = TRUE),
         soiln15_c = base::scale(SoilN15, center = TRUE, scale = FALSE))
```


##Lizard models:------
```{r}
#lizards:
lizard_dat

###centered model, lizards------------
lizard_dat_cs<-
  lizard_dat%>%
    filter(SoilN15>=0)%>%#easy way to remove NAs because all soil values >= 0
  mutate(native_perc_cs = base::scale(native_perc, center = TRUE, scale = TRUE),
         native_perc_c = base::scale(native_perc, center = TRUE, scale = FALSE),
         soiln15_cs = base::scale(SoilN15, center = TRUE, scale = TRUE),
         soiln15_c = base::scale(SoilN15, center = TRUE, scale = FALSE))

lizard_dat_cs_mj<-
 lizard_dat_cs%>%
  mutate(PEU.mj.m2.yr = PEU/1000/10000*365)#convert to same energy units: divide by 1000 for kj to mj, *10,000 for m2 to ha, /365 to go from years to day....so this simplifies to: *10/365 (or = /1000*10000/365)
       

#run centered models: lizards, original energy units-----
lizard_mod_log_c<-
  brm(
 log(PEU) ~ native_perc_c * soiln15_c + (1|date),
  data = lizard_dat_cs, 
  iter = 3000, warmup = 1000, chains = 4, cores = 4,
   control = list(adapt_delta = 0.999, max_treedepth = 15), 
      file = "brms/lizard_mod_log_c") 

print(lizard_mod_log_c) #not many observations (only 14), hence 3 divergent transitions
pp_check(lizard_mod_log_c)#looks okay
plot(lizard_mod_log_c, ask = FALSE)

hypothesis(lizard_mod_log_c, c("native_perc_c>0", #0.24
                                        "soiln15_c>0",#0.66
                                        "native_perc_c:soiln15_c>0")) #0.98


####extract effects: lizards, centered models------
lizard_mod_log_c %>%
  spread_draws(b_native_perc_c, b_soiln15_c, `b_native_perc_c:soiln15_c`) %>%
  median_hdi(b_native_perc_c, b_soiln15_c, `b_native_perc_c:soiln15_c`)
#estimate         lower           upper (95% hdi)
#-0.003728431	  -0.01453456	    0.008198327		 #native percent (at average soil n15)
#0.01694162	    -0.06790722	      0.110402	   #soil n15 (at average native percent)
#0.003091157    	0.0002450153	  0.005766218			  #native percent:soil n15

##extract ground-dwelling emmeans----
range(lizard_dat_cs$native_perc_c, na.rm=TRUE) #-59  41
mean(lizard_dat_cs$native_perc_c, na.rm=TRUE) #0


#at 0, ~50, 100% native forest (min, mean, max), these are the effects of soil n15 on lizards: 
lizard_mod_log_c%>%
emtrends(~native_perc_c, var = "soiln15_c", at = list(native_perc_c = c(-59, 0, 41))) #, type = "response", - need to tell emmeans log-transformed to get response to work: 
# native_perc_c soilN15_c.trend lower.HPD upper.HPD
#           -59         -0.1635  -0.36182     0.020
#             0          0.0169  -0.06884     0.109
#            41          0.1441   0.00577     0.276
#yup, similar results to  to spread_draws and median_hdi above (for mean values)

exp(-0.1635) #0.8491665
exp(-0.36182) #0.6964077
exp(0.020) #1.020201

exp(0.1441) #1.155
exp(0.00577) #1.005787
exp(0.276) #1.317848

range(lizard_dat_cs$soiln15_c, na.rm=TRUE) #-9.203429  6.284571
mean(lizard_dat_cs$soiln15_c, na.rm=TRUE) #0


#at min, mean max soil n15, these are the effects of native forest on lizards: 
lizard_mod_log_c%>%
emtrends(~soiln15_c, var = "native_perc_c", at = list(soiln15_c = c(-9.203429, 0, 6.284571))) #, type = "response", -
# SoilN15 native_perc.trend lower.HPD upper.HPD
#    -9.20            -0.03210  -0.05829  -0.00504
#      0.00            -0.00373  -0.01453   0.00820
#      6.28             0.01568  -0.00485   0.03861
#yup, similar results to non-centered model above, and to spread_draws and median_hdi above (for mean values)

```



#arthropod models: flying and ground-dwelling
```{r}
#overall arthropods: flying-----
fly_arth_mod_log_c<-
  brm(
 log(tot.PEU_kJday) ~ native_perc_c * soiln15_c + (1|island),
  data = arthropod_dat_fly_cs, 
  iter = 3000, warmup = 1000, chains = 4, cores = 4,
   control = list(adapt_delta = 0.999, max_treedepth = 15), 
      file = "brms/fly_arth_mod_log_c") 
print(fly_arth_mod_log_c)

pp_check(fly_arth_mod_log_c)
plot(fly_arth_mod_log_c, ask = FALSE)

hypothesis(fly_arth_mod_log_c, c("native_perc_c>0", #0.69
                                        "soiln15_c>0",#.60
                                        "native_perc_c:soiln15_c>0")) #.18

##extract flying effects------
fly_arth_mod_log_c %>%
  spread_draws(b_native_perc_c, b_soiln15_c, `b_native_perc_c:soiln15_c`) %>%
  median_hdi(b_native_perc_c, b_soiln15_c, `b_native_perc_c:soiln15_c`)
#estimate         lower           upper (95% hdi)
#0.002774197    	-0.008358028	    0.01388863		 #native percent (at average soil n15)
#0.0144214	      -0.1149628      	0.1300489	   #soil n15 (at average native percent)
#-0.000918379	    -0.003047822	    0.001113489			  #native percent:soil n15

##extract flying emmeans----
range(arthropod_dat_fly_cs$native_perc_c, na.rm=TRUE) #-53.46778  46.53222
mean(arthropod_dat_fly_cs$native_perc_c, na.rm=TRUE) #0 ish


#at 0, ~50, 100% native forest (min, mean, max), these are the effects of soil n15 on arthropods: 
fly_arth_mod_log_c%>%
emtrends(~native_perc_c, var = "soiln15_c", at = list(native_perc_c = c(-53.46778, 0, 46.53222))) #, type = "response", - need to tell emmeans log-transformed to get response to work: 
# native_perc_c soilN15_c.trend lower.HPD upper.HPD
#         -53.5          0.0610   -0.0838     0.218
#           0.0          0.0144   -0.1150     0.130
#          46.5         -0.0275   -0.2061     0.139
#yup, similar results to spread_draws and median_hdi above (for mean values)


range(arthropod_dat_fly_cs$soiln15_c, na.rm=TRUE) #-6.915333 11.020667
mean(arthropod_dat_fly_cs$soiln15_c, na.rm=TRUE) #0ish


#at min, mean max soil n15, these are the effects of native forest on arthropods: 
fly_arth_mod_log_c%>%
emtrends(~soiln15_c, var = "native_perc_c", at = list(soiln15_c = c(-6.915333, 0, 11.020667))) #, type = "response", -
# SoilN15 native_perc.trend lower.HPD upper.HPD
# -6.92             0.00914  -0.01004    0.0298
#  0.00             0.00277  -0.00836    0.0139
#  11.02            -0.00758  -0.03244    0.0151
#yup, similar results to spread_draws and median_hdi above (for mean values)


#overall arthropods: ground-----
#run centered models: ground-dwelling-----
ground_arth_mod_log_c<-
  brm(
 log(tot.PEU_kJday) ~ native_perc_c * soiln15_c + (1|island),
  data = arthropod_dat_ground_cs, 
  iter = 3000, warmup = 1000, chains = 4, cores = 4,
   control = list(adapt_delta = 0.999, max_treedepth = 15), 
      file = "brms/ground_arth_mod_log_c") 
print(ground_arth_mod_log_c)

pp_check(ground_arth_mod_log_c)
plot(ground_arth_mod_log_c, ask = FALSE)


hypothesis(ground_arth_mod_log_c, c("native_perc_c>0", #.87
                                        "soiln15_c>0",#0.07
                                        "native_perc_c:soiln15_c>0")) #1.00

##extract ground-dwelling effects------
ground_arth_mod_log_c %>%
  spread_draws(b_native_perc_c, b_soiln15_c, `b_native_perc_c:soiln15_c`) %>%
  median_hdi(b_native_perc_c, b_soiln15_c, `b_native_perc_c:soiln15_c`)
#estimate         lower           upper (95% hdi)
#0.004986617	     -0.004050076	  0.01385365		 #native percent (at average soil n15)
#-0.08611632    	-0.2004247    	0.03526039   #soil n15 (at average native percent)
#0.002046247    	0.0006404748	    	0.00349441		  #native percent:soil n15



##extract ground-dwelling emmeans----
range(arthropod_dat_ground_cs$native_perc_c, na.rm=TRUE) #-56.30769  43.69231
mean(arthropod_dat_ground_cs$native_perc_c, na.rm=TRUE) #0


#at 0, ~50, 100% native forest (min, mean, max), these are the effects of soil n15 on arthropods: 
ground_arth_mod_log_c%>%
emtrends(~native_perc_c, var = "soiln15_c", at = list(native_perc_c = c(-56.30769, 0, 43.69231))) #, type = "response", - need to tell emmeans log-transformed to get response to work: 
# native_perc_c soilN15_c.trend lower.HPD upper.HPD
#         -56.3        -0.20303    -0.325   -0.0568
#           0.0        -0.08612    -0.201    0.0343
#          43.7         0.00458    -0.129    0.1417
#yup, similar results to non-centered model above, and to spread_draws and median_hdi above (for mean values)


range(arthropod_dat_ground_cs$soiln15_c, na.rm=TRUE) #-9.362217  8.573783
mean(arthropod_dat_ground_cs$soiln15_c, na.rm=TRUE) #0


#at min, mean max soil n15, these are the effects of native forest on arthropods: 
ground_arth_mod_log_c%>%
emtrends(~soiln15_c, var = "native_perc_c", at = list(soiln15_c = c(-9.362217, 0, 8.573783))) #, type = "response", -
# SoilN15 native_perc.trend lower.HPD upper.HPD
#     -9.36            -0.01419  -0.02732  0.000407
#      0.00             0.00499  -0.00405  0.013854
#      8.57             0.02251   0.00590  0.040553
#yup, similar results to non-centered model above, and to spread_draws and median_hdi above (for mean values)

#back transform for high native forest:
exp(0.02251) #1.022765
exp(0.00590) #1.005917
exp(0.040553) #1.041387

#back transform for low native forest:
exp(-0.01419) #0.9859102
exp(-0.02732) #0.9730498
exp(0.000407) #1.000407

1-exp(-0.01419) #0.0140898 decrease
1-exp(-0.02732) #0.02695018 decrease
exp(0.000407)-1 #0.0004070828 increase

```


#arthropod models:ground-dwelling functional groups:
```{r}
#functional groups, ground-dwelling:----
herb_ground_arth_mod_log_c<-
  brm(
 log(phytophag.PEU_kJday) ~ native_perc_c * soiln15_c + (1|island),
  data = arthropod_dat_ground_cs, 
  iter = 3000, warmup = 1000, chains = 4, cores = 4,
   control = list(adapt_delta = 0.999, max_treedepth = 15), 
      file = "brms/herb_ground_arth_mod_log_c") 


print(herb_ground_arth_mod_log_c) #worked fine

pp_check(herb_ground_arth_mod_log_c) #looks good
plot(herb_ground_arth_mod_log_c, ask = FALSE)

hypothesis(herb_ground_arth_mod_log_c, c("native_perc_c>0", #.84
                                        "soiln15_c>0",#0.10
                                        "native_perc_c:soiln15_c>0")) #0.97
#okay, similar effects as above - very strong interaction

#extract some emmeans estimates (herbivores):----
#at 0, ~50, 100% native forest (min, mean, max), these are the effects of soil n15 on herbivores: 
herb_ground_arth_mod_log_c%>%
emtrends(~native_perc_c, var = "soiln15_c", at = list(native_perc_c = c(-56.30769, 0, 43.69231))) #, type = "response", - need to tell emmeans log-transformed to get response to work: 
# native_perc_c soilN15_c.trend lower.HPD upper.HPD
#         -56.3          -0.172    -0.350    0.0171
#           0.0          -0.102    -0.274    0.0825
#          43.7          -0.048    -0.231    0.1408
#yup, similar results to total ground model, except n15 trending NEGATIVE across all native forest % (just weaker effect size at higher native forest)

#at min, mean max soil n15, these are the effects of native forest on herbivores: 
herb_ground_arth_mod_log_c%>%
emtrends(~soiln15_c, var = "native_perc_c", at = list(soiln15_c = c(-9.362217, 0, 8.573783))) #, type = "response", -
# SoilN15 native_perc.trend lower.HPD upper.HPD
#   -9.36            -0.00732 -0.018768   0.00415
#      0.00           0.00388 -0.003779   0.01217
#     8.57            0.01404 -0.000398   0.03057
#yup, similar results to total ground model, except all 95% HPDIs overlap 0 (even at high soil n15 where trending positive)



####now with ground-dwelling decomposition:---- 
#‘saprophagous’ + ‘detritophagous’
arthropod_dat_ground_cs_det<-
  arthropod_dat_ground_cs%>%
  rowwise()%>%
  mutate(decomposer.PEU_kjday = saprophag.PEU_kJday + detritophag.PEU_kJday)%>%
  ungroup()

det_ground_arth_mod_log_c<-
  brm(
 log(decomposer.PEU_kjday) ~ native_perc_c * soiln15_c + (1|island),
  data = arthropod_dat_ground_cs_det, 
  iter = 3000, warmup = 1000, chains = 4, cores = 4,
   control = list(adapt_delta = 0.999, max_treedepth = 15), 
      file = "brms/det_ground_arth_mod_log_c") 


print(det_ground_arth_mod_log_c) #worked fine

pp_check(det_ground_arth_mod_log_c) #looks good
plot(det_ground_arth_mod_log_c, ask = FALSE)

hypothesis(det_ground_arth_mod_log_c, c("native_perc_c>0", #.87
                                        "soiln15_c>0",#0.04
                                        "native_perc_c:soiln15_c>0")) #0.99
#okay, similar effects as above - very strong interaction

#extract some emmeans estimates (detritivores):----
#at 0, ~50, 100% native forest (min, mean, max), these are the effects of soil n15 on herbivores: 
det_ground_arth_mod_log_c%>%
emtrends(~native_perc_c, var = "soiln15_c", at = list(native_perc_c = c(-56.30769, 0, 43.69231))) #, type = "response", - need to tell emmeans log-transformed to get response to work: 
# native_perc_c soilN15_c.trend lower.HPD upper.HPD
#        -56.3        -0.24192    -0.389   -0.0861
#           0.0        -0.10246    -0.223    0.0163
#          43.7         0.00493    -0.150    0.1494
#yup, similar results to total ground model and herbivores, no1 n15 trending positive at high native forest % again (similar to overall)

#at min, mean max soil n15, these are the effects of native forest on detritivores: 
det_ground_arth_mod_log_c%>%
emtrends(~soiln15_c, var = "native_perc_c", at = list(soiln15_c = c(-9.362217, 0, 8.573783))) #, type = "response", -
# SoilN15 native_perc.trend lower.HPD upper.HPD
#      -9.36            -0.01617  -0.03458    0.0027
#      0.00             0.00643  -0.00529    0.0181
#      8.57             0.02758   0.00524    0.0482
#yup, similar results to total ground model


#now with predators (zoophag)----
pred_ground_arth_mod_c<-
  brm(
 log(zoophag.PEU_kJday) ~ native_perc_c * soiln15_c+ (1|island),
  data = arthropod_dat_ground_cs, 
  iter = 3000, warmup = 1000, chains = 4, cores = 4,
   control = list(adapt_delta = 0.999, max_treedepth = 15), 
      file = "brms/pred_ground_arth_mod_c") 


print(pred_ground_arth_mod_c) #worked fine

pp_check(pred_ground_arth_mod_c) #looks good
plot(pred_ground_arth_mod_c, ask = FALSE)

hypothesis(pred_ground_arth_mod_c, c("native_perc_c>0", #.99
                                        "soiln15_c>0",#0.10
                                        "native_perc_c:soiln15_c>0")) #1.0
#okay, similar effects as above - very strong interaction

#extract some emmeans estimates (herbivores):----
#at 0, ~50, 100% native forest (min, mean, max), these are the effects of soil n15 on herbivores: 
pred_ground_arth_mod_c%>%
emtrends(~native_perc_c, var = "soiln15_c", at = list(native_perc_c = c(-56.30769, 0, 43.69231))) #, type = "response", - need to tell emmeans log-transformed to get response to work: 
# native_perc_c soilN15_c.trend lower.HPD upper.HPD
#        -56.3         -0.1919    -0.331   -0.0522
#           0.0         -0.0784    -0.208    0.0522
#          43.7          0.0093    -0.135    0.1411
#yup, similar results to total ground model and detritivore model

#at min, mean max soil n15, these are the effects of native forest on herbivores: 
pred_ground_arth_mod_c%>%
emtrends(~soiln15_c, var = "native_perc_c", at = list(soiln15_c = c(-9.362217, 0, 8.573783))) #, type = "response", -
# SoilN15 native_perc.trend lower.HPD upper.HPD
#     -9.36            -0.01152 -0.020850  -0.00244
#      0.00             0.00693  0.000733   0.01319
 #     8.57             0.02389  0.011238   0.03555
#yup, similar results to total ground model and detirtivore model 



```

#use darker colors for plotting, so create new palette:
```{r}
my_palette <- brewer.pal(name="YlOrBr",n=4)[2:4]

```


###plot - lizards
```{r}
me_liz_int_log<-conditional_effects(lizard_mod_log_c, prob = .75, 'native_perc_c:soiln15_c', plot = FALSE)[[1]]


mean(lizard_dat_cs$SoilN15)#9.525429
mean(lizard_dat_cs$native_perc)#59


##try just changing labels for mj/m2/year:-----
# UNITS WERE IN DAYS AND WE HAVE TO GO TO YEARS, SO:
#mj/m2/year = divide by 1000 for kj to mj, /10,000 for ha to m2, *365 to go from days to years....so this  = /1000/10000*365)


me_liz_int_log<-conditional_effects(lizard_mod_log_c, prob = .75, 'native_perc_c:soiln15_c', plot = FALSE)[[1]]


mean(lizard_dat_cs$SoilN15)#9.525429
mean(lizard_dat_cs$native_perc)#59


#so use kj/m2/year: -------
me_liz_int_log_unscale<-
  me_liz_int_log%>%
  mutate(SoilN15 = soiln15_c + 9.525429,
         native_perc =native_perc_c +59 ,
          Soil_fact = as.factor(round(SoilN15, 0)))%>%
  mutate(Soil_fact = fct_recode(Soil_fact, low = "4", mid = "10", high = "15"))%>% #values from table
  mutate(Soil_fact = fct_relevel(Soil_fact,  "low", "mid", "high"))%>%
  mutate(PEU.kj.m2.yr = log(exp(estimate__)/10000*365),
         upper.kj.m2.yr = log(exp(upper__)/10000*365),
         lower.kj.m2.yr = log(exp(lower__)/10000*365))


lizard_vs_forest_soiln15_plot5<-
lizard_dat_cs_mj %>%
 mutate(PEU.kj.m2.yr = PEU/10000*365)%>%
 ggplot(aes(x = native_perc, y = log(PEU.kj.m2.yr))) +
     geom_ribbon(data = me_liz_int_log_unscale, aes(x = native_perc, y = PEU.kj.m2.yr, ymin = lower.kj.m2.yr, ymax = upper.kj.m2.yr, fill = Soil_fact), lwd = 0, alpha = .2) +
geom_line(data = me_liz_int_log_unscale, aes(x = native_perc, y = PEU.kj.m2.yr, colour = Soil_fact), lwd = 1.2) +
  scale_fill_manual(values = my_palette, name = "")+
    scale_colour_manual(values = my_palette, name = "")+
    #scale_colour_brewer(direction = 1, name = "", palette = "YlOrBr")+#"YlOrRd"
 # scale_fill_brewer(direction = 1,  name = "", palette = "YlOrBr")+#"YlOrRd"
         guides(color = guide_legend(direction = "horizontal",  barwidth = .8,   
    barheight = .1, override.aes = list(lwd = .4), order = 0)) +
    new_scale_fill()+
       geom_point(aes(fill =  SoilN15), pch = 21, size = 2, alpha = .9) + #, size = .8 as.factor(Birds)
       scale_fill_distiller(direction = 1,  palette = "YlOrBr" )+ #"YlOrRd"
labs(fill = expression(Soil~delta^15~N))+
  guides(fill = guide_colorbar(direction = "horizontal",  barwidth = 6,   
    barheight = .2, order = 1, title.position = "top" )) +
  xlab("Native vegetation cover (%)")+    ylab(expression(Lizard~energy~flow~(KJ~m^-2~yr^-1)))+
  scale_y_continuous(labels = c(1, 2, 4, 8, 16), breaks = c(log(1), log(2), log(4), log(8), log(16)))+
  theme_bw()+
    theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
            text = element_text(size = 10),
        legend.position=c(.5, .86),
 legend.box = "vertical",
        legend.direction="horizontal",
               legend.key.width=unit(0.5,"cm"),
        legend.key.spacing.y = unit(-6, "pt"),
      #   legend.key.spacing.x = unit(-6, "pt"),
        legend.spacing = unit(-6, "pt"),
       legend.text = element_text(size = 10, margin = margin(l=0, b = 0)), #size = 6
      legend.title = element_text(size = 10), #, margin = margin(b=.5) #size = 6
      legend.box.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"),
        legend.background = element_blank(),
         #legend.box.background = element_rect(),
      legend.box.background = element_blank())
lizard_vs_forest_soiln15_plot5

```


###plot arthropods: ground-dwelling:
```{r}
#ground-----
me_ground_int_log<-conditional_effects(ground_arth_mod_log_c, prob = .75, 'native_perc_c:soiln15_c', plot = FALSE)[[1]]


mean(arthropod_dat_ground_cs$SoilN15)#9.684217
mean(arthropod_dat_ground_cs$native_perc)#56.30769



#####convert to kj/year----------
me_ground_int_log_unscale2<-
  me_ground_int_log%>%
  mutate(SoilN15 = soiln15_c + 9.684217,
         native_perc =native_perc_c +56.30769, 
         Soil_fact = as.factor(round(SoilN15, 0)))%>%
  mutate(Soil_fact = fct_recode(Soil_fact, low = "3", mid = "10", high = "16"))%>%
  mutate(Soil_fact = fct_relevel(Soil_fact, "low", "mid", "high"))%>%
  mutate(est_kj_yr = log(exp(estimate__)*365),
         upper.kj.yr = log(exp(upper__)*365),
         lower.kj.yr = log(exp(lower__)*365))


ground_arthropod_vs_forest_soiln15_plot4<-
arthropod_dat_ground_cs %>%
  mutate(PEU_kj_yr = tot.PEU_kJday*365)%>%
  ggplot(aes(x = native_perc, y = log(PEU_kj_yr))) +
geom_line(data = me_ground_int_log_unscale2, aes(x = native_perc, y = est_kj_yr, colour = Soil_fact), lwd = 1.2) +
      geom_ribbon(data = me_ground_int_log_unscale2, aes(x = native_perc, y = est_kj_yr, ymin = lower.kj.yr, ymax=upper.kj.yr, fill = Soil_fact), alpha = .2,lwd = 0)+ # fill = "gray"
 scale_fill_manual(values = my_palette, name = "")+
    scale_colour_manual(values = my_palette, name = "")+
    #scale_colour_brewer(direction = 1, name = "", palette = "YlOrBr")+#"YlOrRd"
 # scale_fill_brewer(direction = 1,  name = "", palette = "YlOrBr")+#"YlOrRd"
       guides(color = guide_legend(direction = "horizontal",  barwidth = .8,   
    barheight = .1, override.aes = list(lwd = .4), order = 0)) +
    new_scale_fill()+
    new_scale_fill()+
 geom_jitter(aes(fill = SoilN15), pch = 21, size = 2, alpha = .8, height = 0, width = 2) + #, size = .8
    scale_fill_distiller(direction = 1, palette = "YlOrBr", name = expression(Soil~delta^15~N))+
   guides(fill = guide_colorbar(direction = "horizontal",  barwidth = 6,   
    barheight = .2, order = 1, title.position = "top" )) +
  xlab("Native vegetation cover (%)")+
#  ylab(expression(atop("Ground-dwelling arthropod", paste(energy~requirements~(log~kj~day^-1)))))+  
    ylab(expression(Ground-dwelling~arthropod~energy~flow~(KJ~yr^-1)))+  
  scale_y_continuous(labels = c(.001, .01, .1, 1), breaks = c(log(.001), log(.01), log(.1), log(1)))+
  # scale_y_continuous(labels = c(exp(0),exp(1),exp(-1),exp(-3),exp(-10)), breaks = c(0,1,-1,-3,-10))+
  #1.1 = log(1.1) - certy close to 1 ....
  theme_bw()+
    theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
            text = element_text(size = 10),
        legend.position=c(.7, .18),
 legend.box = "vertical",
        legend.direction="horizontal",
               legend.key.width=unit(0.5,"cm"),
        legend.key.spacing.y = unit(-6, "pt"),
      #   legend.key.spacing.x = unit(-6, "pt"),
        legend.spacing = unit(-6, "pt"),
       legend.text = element_text(size = 10, margin = margin(l=0, b = 0)), #size = 6
      legend.title = element_text(size = 10), #, margin = margin(b=.5) #size = 6
      legend.box.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"),
        legend.background = element_blank(),
         #legend.box.background = element_rect(),
      legend.box.background = element_blank())
    
ground_arthropod_vs_forest_soiln15_plot4


```


###plot arthropods: FLYING:
```{r}
#fly-----
me_fly_int_log<-conditional_effects(fly_arth_mod_log_c, prob = .75, 'native_perc_c:soiln15_c', plot = FALSE)[[1]]


mean(arthropod_dat_fly_cs$SoilN15)#7.237333
mean(arthropod_dat_fly_cs$native_perc)#53.46778




##new - kj/year-----
me_fly_int_log_unscale2<-
  me_fly_int_log%>%
  mutate(SoilN15 = soiln15_c + 7.237333,
         native_perc =native_perc_c +53.46778, 
         Soil_fact = as.factor(round(SoilN15, 0)))%>%
  mutate(Soil_fact = fct_recode(Soil_fact, low = "1", mid = "7", high = "13"))%>%
  mutate(Soil_fact = fct_relevel(Soil_fact,  "low", "mid", "high"))%>%
  mutate(est_kj_yr = log(exp(estimate__)*365),
         upper.kj.yr = log(exp(upper__)*365),
         lower.kj.yr = log(exp(lower__)*365))


fly_arthropod_vs_forest_soiln15_plot3<-
arthropod_dat_fly_cs %>%
  mutate(PEU_kj_yr = tot.PEU_kJday*365)%>%
  ggplot(aes(x = native_perc, y = log(PEU_kj_yr))) +
geom_line(data = me_fly_int_log_unscale2, aes(x = native_perc, y = est_kj_yr, colour = Soil_fact), lwd = 1.2) +
      geom_ribbon(data = me_fly_int_log_unscale2, aes(x = native_perc, y = est_kj_yr, ymin = lower.kj.yr, ymax=upper.kj.yr, fill = Soil_fact), alpha = .2,lwd = 0)+ # fill = "gray"
     scale_fill_manual(values = my_palette, name = "")+
    scale_colour_manual(values = my_palette, name = "")+
    #scale_colour_brewer(direction = 1, name = "", palette = "YlOrBr")+#"YlOrRd"
 # scale_fill_brewer(direction = 1,  name = "", palette = "YlOrBr")+#"YlOrRd"
     guides(color = guide_legend(direction = "horizontal",  barwidth = .8,   
    barheight = .1, override.aes = list(lwd = .4), order = 0)) +
    new_scale_fill()+
 geom_jitter(aes(fill = SoilN15), pch = 21, size = 2, alpha = .8, height = 0, width = 2) + #, size = .8
    scale_fill_distiller(direction = 1, palette = "YlOrBr", name = expression(Soil~delta^15~N))+
   guides(fill = guide_colorbar(direction = "horizontal",  barwidth = 6,   
    barheight = .2, order = 1, title.position = "top" )) +
  xlab("Native vegetation cover (%)")+
#  ylab(expression(atop("Flying arthropod", paste(energy~requirements~(log~kj~day^-1)))))+  
    ylab(expression(Flying~arthropod~energy~flow~(KJ~yr^-1)))+  
   scale_y_continuous(labels = c(.05, .1, .2, .4), breaks = c( log(.05), log(.1), log(0.2), log(.4)))+
  # scale_y_continuous(labels = c(exp(0),exp(1),exp(-1),exp(-3),exp(-10)), breaks = c(0,1,-1,-3,-10))+
  #1.1 = log(1.1) - certy close to 1 ....
  theme_bw()+
    theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
            text = element_text(size = 10),
        legend.position=c(.7, .18),
 legend.box = "vertical",
        legend.direction="horizontal",
               legend.key.width=unit(0.5,"cm"),
        legend.key.spacing.y = unit(-6, "pt"),
      #   legend.key.spacing.x = unit(-6, "pt"),
        legend.spacing = unit(-6, "pt"),
       legend.text = element_text(size = 10, margin = margin(l=0, b = 0)), #size = 6
      legend.title = element_text(size = 10), #, margin = margin(b=.5) #size = 6
      legend.box.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"),
        legend.background = element_blank(),
         #legend.box.background = element_rect(),
      legend.box.background = element_blank())
    
fly_arthropod_vs_forest_soiln15_plot3


```

#ground functional group plots:-----
```{r}

####now with ground-dwelling decomposition:---- 
me_decomp_int_log<-conditional_effects(det_ground_arth_mod_log_c, prob = .75, 'native_perc_c:soiln15_c', plot = FALSE)[[1]]


mean(arthropod_dat_ground_cs_det$SoilN15)#9.684217
mean(arthropod_dat_ground_cs_det$native_perc)#56.30769


##new - kj/year-----
me_decomp_int_log_unscale2<-
  me_decomp_int_log%>%
  mutate(SoilN15 = soiln15_c + 9.684217,
         native_perc =native_perc_c +56.30769, 
         Soil_fact = as.factor(round(SoilN15, 0)))%>%
  mutate(Soil_fact = fct_recode(Soil_fact, low = "3", mid = "10", high = "16"))%>%
  mutate(Soil_fact = fct_relevel(Soil_fact,  "low", "mid", "high"))%>%
  mutate(est_kj_yr = log(exp(estimate__)*365),
         upper.kj.yr = log(exp(upper__)*365),
         lower.kj.yr = log(exp(lower__)*365))


decomp_arthropod_vs_forest_soiln15_plot2<-
arthropod_dat_ground_cs_det %>%
  mutate(decomposer.PEU_kj_yr= decomposer.PEU_kjday*365)%>%
  ggplot(aes(x = native_perc, y = log(decomposer.PEU_kj_yr))) +
geom_line(data = me_decomp_int_log_unscale2, aes(x = native_perc, y = est_kj_yr, colour = Soil_fact), lwd = 1.2) +
      geom_ribbon(data = me_decomp_int_log_unscale2, aes(x = native_perc, y = est_kj_yr, ymin = lower.kj.yr, ymax=upper.kj.yr, fill = Soil_fact), alpha = .2,lwd = 0)+ # fill = "gray"
     scale_fill_manual(values = my_palette, name = "")+
    scale_colour_manual(values = my_palette, name = "")+
    #scale_colour_brewer(direction = 1, name = "", palette = "YlOrBr")+#"YlOrRd"
 # scale_fill_brewer(direction = 1,  name = "", palette = "YlOrBr")+#"YlOrRd"
   guides(color = guide_legend(direction = "horizontal",  barwidth = .8,   
    barheight = .1, override.aes = list(lwd = .4), order = 0)) +
    new_scale_fill()+
 geom_jitter(aes(fill = SoilN15), pch = 21, size = 2, alpha = .8, height = 0, width = 2) + #, size = .8
    scale_fill_distiller(direction = 1, palette = "YlOrBr", name = expression(Soil~delta^15~N))+
   guides(fill = guide_colorbar(direction = "horizontal",  barwidth = 6,   
    barheight = .2, order = 1, title.position = "top" )) +
  xlab("Native vegetation cover (%)")+
#  ylab(expression(atop("Ground-dwelling arthropod", paste(energy~requirements~(log~kj~day^-1)))))+  
    ylab(expression(Decomposer~energy~flow~(KJ~yr^-1)))+  
   scale_y_continuous(labels = c(.00001, 0.0001, .001, .01, .1, "1.0"), breaks = c(log(.00001), log(0.0001), log(0.001), log(.01), log(.1), 0))+
  # scale_y_continuous(labels = c(exp(0),exp(1),exp(-1),exp(-3),exp(-10)), breaks = c(0,1,-1,-3,-10))+
  #1.1 = log(1.1) - certy close to 1 ....
  theme_bw()+
    theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
            text = element_text(size = 10),
        legend.position=c(.7, .18),
 legend.box = "vertical",
        legend.direction="horizontal",
               legend.key.width=unit(0.5,"cm"),
        legend.key.spacing.y = unit(-6, "pt"),
      #   legend.key.spacing.x = unit(-6, "pt"),
        legend.spacing = unit(-6, "pt"),
       legend.text = element_text(size = 10, margin = margin(l=0, b = 0)), #size = 6
      legend.title = element_text(size = 10), #, margin = margin(b=.5) #size = 6
      legend.box.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"),
        legend.background = element_blank(),
         #legend.box.background = element_rect(),
      legend.box.background = element_blank())
decomp_arthropod_vs_forest_soiln15_plot2




#herbivores:----
me_herb_int_log<-conditional_effects(herb_ground_arth_mod_log_c, prob = .75, 'native_perc_c:soiln15_c', plot = FALSE)[[1]]


mean(arthropod_dat_ground_cs$SoilN15)#9.684217
mean(arthropod_dat_ground_cs$native_perc)#56.30769


##new-----
me_herb_int_log_unscale2<-
  me_herb_int_log%>%
  mutate(SoilN15 = soiln15_c + 9.684217,
         native_perc =native_perc_c +56.30769, 
         Soil_fact = as.factor(round(SoilN15, 0)))%>%
  mutate(Soil_fact = fct_recode(Soil_fact, low = "3", mid = "10", high = "16"))%>%
  mutate(Soil_fact = fct_relevel(Soil_fact,  "low", "mid", "high"))%>%
  mutate(est_kj_yr = log(exp(estimate__)*365),
         upper.kj.yr = log(exp(upper__)*365),
         lower.kj.yr = log(exp(lower__)*365))


herb_arthropod_vs_forest_soiln15_plot2<-
arthropod_dat_ground_cs %>%
  mutate(phytophag.PEU_kj_yr = phytophag.PEU_kJday*365)%>%
  ggplot(aes(x = native_perc, y = log(phytophag.PEU_kj_yr))) +
geom_line(data = me_ground_int_log_unscale2, aes(x = native_perc, y = est_kj_yr, colour = Soil_fact), lwd = 1.2) +
      geom_ribbon(data = me_ground_int_log_unscale2, aes(x = native_perc, y = est_kj_yr, ymin = lower.kj.yr, ymax=upper.kj.yr, fill = Soil_fact), alpha = .2,lwd = 0)+ # fill = "gray"
 scale_fill_manual(values = my_palette, name = "")+
    scale_colour_manual(values = my_palette, name = "")+
    #scale_colour_brewer(direction = 1, name = "", palette = "YlOrBr")+#"YlOrRd"
 # scale_fill_brewer(direction = 1,  name = "", palette = "YlOrBr")+#"YlOrRd"
    guides(color = guide_legend(direction = "horizontal",  barwidth = .8,   
    barheight = .1, override.aes = list(lwd = .4), order = 0)) +
    new_scale_fill()+
 geom_jitter(aes(fill = SoilN15), pch = 21, size = 2, alpha = .8, height = 0, width = 2) + #, size = .8
    scale_fill_distiller(direction = 1, palette = "YlOrBr", name = expression(Soil~delta^15~N))+
      guides(fill = guide_colorbar(direction = "horizontal",  barwidth = 6,   
    barheight = .2, order = 1, title.position = "top" )) +
  xlab("Native vegetation cover (%)")+
#  ylab(expression(atop("Ground-dwelling arthropod", paste(energy~requirements~(log~kj~day^-1)))))+  
    ylab(expression(Herbivore~energy~flow~(KJ~yr^-1)))+  
   scale_y_continuous(labels = c(.0001, .001, .01, .1, "1.0"), breaks = c(log(0.0001), log(0.001), log(.01), log(.1), 0))+
  # scale_y_continuous(labels = c(exp(0),exp(1),exp(-1),exp(-3),exp(-10)), breaks = c(0,1,-1,-3,-10))+
  #1.1 = log(1.1) - certy close to 1 ....
  theme_bw()+
    theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
            text = element_text(size = 10),
        legend.position=c(.7, .18),
 legend.box = "vertical",
        legend.direction="horizontal",
               legend.key.width=unit(0.5,"cm"),
        legend.key.spacing.y = unit(-6, "pt"),
      #   legend.key.spacing.x = unit(-6, "pt"),
        legend.spacing = unit(-6, "pt"),
       legend.text = element_text(size = 10, margin = margin(l=0, b = 0)), #size = 6
      legend.title = element_text(size = 10), #, margin = margin(b=.5) #size = 6
      legend.box.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"),
        legend.background = element_blank(),
         #legend.box.background = element_rect(),
      legend.box.background = element_blank())
herb_arthropod_vs_forest_soiln15_plot2



#try with predators (zoophag)----
me_pred_int_log<-conditional_effects(pred_ground_arth_mod_c, prob = .75, 'native_perc_c:soiln15_c', plot = FALSE)[[1]]


mean(arthropod_dat_ground_cs$SoilN15)#9.684217
mean(arthropod_dat_ground_cs$native_perc)#56.30769


##new-----
me_pred_int_log_unscale2<-
  me_pred_int_log%>%
  mutate(SoilN15 = soiln15_c + 9.684217,
         native_perc =native_perc_c +56.30769, 
         Soil_fact = as.factor(round(SoilN15, 0)))%>%
  mutate(Soil_fact = fct_recode(Soil_fact, low = "3", mid = "10", high = "16"))%>%
  mutate(Soil_fact = fct_relevel(Soil_fact,  "low", "mid", "high"))%>%
  mutate(est_kj_yr = log(exp(estimate__)*365),
         upper.kj.yr = log(exp(upper__)*365),
         lower.kj.yr = log(exp(lower__)*365))


pred_arthropod_vs_forest_soiln15_plot2<-
arthropod_dat_ground_cs %>%
  mutate(zoophag.PEU_kj_day = zoophag.PEU_kJday*365)%>%
  ggplot(aes(x = native_perc, y = log(zoophag.PEU_kj_day))) +
geom_line(data = me_pred_int_log_unscale2, aes(x = native_perc, y = est_kj_yr, colour = Soil_fact), lwd = 1.2) +
      geom_ribbon(data = me_pred_int_log_unscale2, aes(x = native_perc, y = est_kj_yr, ymin = lower.kj.yr, ymax=upper.kj.yr, fill = Soil_fact), alpha = .2,lwd = 0)+ # fill = "gray"
    scale_fill_manual(values = my_palette, name = "")+
    scale_colour_manual(values = my_palette, name = "")+
    #scale_colour_brewer(direction = 1, name = "", palette = "YlOrBr")+#"YlOrRd"
 # scale_fill_brewer(direction = 1,  name = "", palette = "YlOrBr")+#"YlOrRd"
          guides(color = guide_legend(direction = "horizontal",  barwidth = .8,   
    barheight = .1, override.aes = list(lwd = .4), order = 0)) +
    new_scale_fill()+
 geom_jitter(aes(fill = SoilN15), pch = 21, size = 2, alpha = .8, height = 0, width = 2) + #, size = .8
    scale_fill_distiller(direction = 1, palette = "YlOrBr", name = expression(Soil~delta^15~N))+
    guides(fill = guide_colorbar(direction = "horizontal",  barwidth = 6,   
    barheight = .2, order = 1, title.position = "top" )) +
  xlab("Native vegetation cover (%)")+
#  ylab(expression(atop("Ground-dwelling arthropod", paste(energy~requirements~(log~kj~day^-1)))))+  
    ylab(expression(Predator~energy~flow~(KJ~yr^-1)))+  
   scale_y_continuous(labels = c(.0001, .001, .01, .1, "1.0", "4.0"), breaks = c(log(0.0001), log(0.001), log(.01), log(.1), 0, log(4)))+
  # scale_y_continuous(labels = c(exp(0),exp(1),exp(-1),exp(-3),exp(-10)), breaks = c(0,1,-1,-3,-10))+
  #1.1 = log(1.1) - certy close to 1 ....
  theme_bw()+
    theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
            text = element_text(size = 10),
        legend.position=c(.7, .18),
 legend.box = "vertical",
        legend.direction="horizontal",
               legend.key.width=unit(0.5,"cm"),
        legend.key.spacing.y = unit(-6, "pt"),
      #   legend.key.spacing.x = unit(-6, "pt"),
        legend.spacing = unit(-6, "pt"),
       legend.text = element_text(size = 10, margin = margin(l=0, b = 0)), #size = 6
      legend.title = element_text(size = 10), #, margin = margin(b=.5) #size = 6
      legend.box.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"),
        legend.background = element_blank(),
         #legend.box.background = element_rect(),
      legend.box.background = element_blank())
  
pred_arthropod_vs_forest_soiln15_plot2


 
```


##combine plots and save------
```{r}

pred_arthropod_vs_forest_soiln15_plot2
herb_arthropod_vs_forest_soiln15_plot2
decomp_arthropod_vs_forest_soiln15_plot2
fly_arthropod_vs_forest_soiln15_plot3
ground_arthropod_vs_forest_soiln15_plot4
lizard_vs_forest_soiln15_plot5


Supp_Fig_2<-plot_grid(lizard_vs_forest_soiln15_plot5, fly_arthropod_vs_forest_soiln15_plot3, ground_arthropod_vs_forest_soiln15_plot4, pred_arthropod_vs_forest_soiln15_plot2, herb_arthropod_vs_forest_soiln15_plot2, decomp_arthropod_vs_forest_soiln15_plot2, 
                      labels = "auto", label_fontface = "bold", nrow = 3, hjust = c(-2.5, -2.5, -2.5, -2.5, -4.5, -5.5))
Supp_Fig_2

#ggsave(Supp_Fig_2, filename = "../figures/Supp_Fig_Arth_Liz.jpg", width = 8, height = 10)


```



#check sample sizes:
```{r}
arthropod_dat_ground_cs%>%
  group_by(island)%>%
  summarize(count_n = length(tot.PEU_kJday))
#46 samples across 8 islands


arthropod_dat_fly_cs%>%
  group_by(island)%>%
  summarize(count_n = length(tot.PEU_kJday))
#15 samples across 8 islands


lizard_dat_cs%>%
  group_by(island)%>%
  summarize(count_n = length(PEU))
#14 samples across 7 islands


```

