---
title: "Fig4-resilience-R1"
author: "CEB"
date: '2024-06-04'
output: html_document
---

Revisions 1 changes - (1) check group-level effects (2) slight change to forereef reef accretion values, so re-run and re-plot (no change to lagoon values)


#load packages
```{r}
library(tidyverse)

#for bayesian analysis:
library(brms)
library(tidybayes)

library(emmeans)

library(cowplot)

```


#load data
```{r}
#reef resilience data
reef_res_dat<-read.csv("../data/Fig4_reef_related_resilience.csv")


#island data (all that's necessary, beacause only Chagos)
isl_dat<-read.csv("../data/Energetics_islands_Oct.csv")%>%
   mutate(Site.Name = Island)
isl_dat

```



#combine data
```{r}
reef_res_site_dat<-
  right_join(select(isl_dat, c(Region, Atoll, Island, Site.Name, Rats)), reef_res_dat, by = "Site.Name")

reef_res_site_dat
#n = 48


```


#bayesian models for reef-wide sediment production potential - compare location (forereef versus lagoon) and rat status
```{r}

#use log models - sampling way better and then can estimate multiplicative effect (as in figure)
reef_res_site_dat2<-
  reef_res_site_dat%>%
  mutate(log_sed_delivery = log(sediment_delivery_m3_m_yr))
  

reef_sed_rat_mod_group_log2<-
  brm(
 log_sed_delivery~Rats*Location + (1|Atoll),
  data = reef_res_site_dat2, 
  iter = 3000, warmup = 1000, chains = 4, cores = 4,
   control = list(adapt_delta = 0.999, max_treedepth = 15), 
      file = "brms/reef_sed_rat_mod_group_log2") 
print(reef_sed_rat_mod_group_log2) # worked :)

pp_check(reef_sed_rat_mod_group_log2) #looks good
plot(reef_sed_rat_mod_group_log2, ask = FALSE)

hypothesis(reef_sed_rat_mod_group_log2, c("Ratsyes+Ratsyes:Locationlagoon <0", #0.97 - should be ratty effect for lagoon
                                          "Ratsyes<0", #.93 should be ratty effect for fore-reef
                                          "Locationlagoon>0", #.96 test for lagoon effect around non-ratty islands 
                                          "Locationlagoon+Ratsyes:Locationlagoon >0")) #.96 test for lagoon effect (around ratty islands) 

```


#extract estimates from  model for sediment production potential:
```{r}

reef_sed_rat_mod_group_log2

##extract emmeans----
reef_sed_rat_mod_group_log2.rg <- update(ref_grid(reef_sed_rat_mod_group_log2), tran = "log") #THIS LINE IS CLUTCH*** Now don't have to use link transformations, can use log response and still backtransform with emmeans


#full output for interaction effect:
reef_sed_rat_mod_group_log2.rg%>%
emmeans(c("Location", "Rats"),
        type="response")%>%
      contrast("revpairwise") 
# contrast                                   ratio lower.HPD upper.HPD
# lagoon no / forereef shallow no            2.667    0.5829     6.761
# forereef shallow yes / forereef shallow no 0.439    0.0839     1.135
# forereef shallow yes / lagoon no           0.165    0.0345     0.445
# lagoon yes / forereef shallow no           0.957    0.2261     2.384
# lagoon yes / lagoon no                     0.356    0.0731     0.900
# lagoon yes / forereef shallow yes          2.173    0.4379     5.590


#full output for interaction effect (reversed order):
reef_sed_rat_mod_group_log2.rg%>%
emmeans(c("Location", "Rats"),
        type="response")%>%
      contrast("pairwise")
# contrast                                   ratio lower.HPD upper.HPD
# forereef shallow no / lagoon no            0.375    0.0802     0.938
# forereef shallow no / forereef shallow yes 2.276    0.4965     5.880
# forereef shallow no / lagoon yes           1.045    0.2384     2.606
# lagoon no / forereef shallow yes           6.066    1.0301    15.630
# lagoon no / lagoon yes                     2.810    0.6241     7.051
# forereef shallow yes / lagoon yes          0.460    0.1074     1.209


###each group: 
reef_sed_rat_mod_group_log2.rg%>%
emmeans("Rats", 
        by=c("Location"),
        type="response")
#Location = forereef shallow:
# Rats response lower.HPD upper.HPD
# no     0.0618   0.00379    0.1794
# yes    0.0271   0.00186    0.0824

#Location = lagoon:
# Rats response lower.HPD upper.HPD
# no     0.1632   0.01130    0.4788
# yes    0.0585   0.00244    0.1747

#Point estimate displayed: median 
#Results are back-transformed from the log scale 
#HPD interval probability: 0.95 

```


#bayesian models for reef accretion
```{r}
#can't log response because it goes below 0. updated forereef values

reef_accr_rat_mod_group2<-
  brm(
 reef_accretion_2.0_mm_yr_corrected~Rats*Location + (1|Atoll),
  data = reef_res_site_dat, 
  iter = 3000, warmup = 1000, chains = 4, cores = 4,
   control = list(adapt_delta = 0.999, max_treedepth = 15), 
      file = "brms/reef_accr_rat_mod_group2") 
print(reef_accr_rat_mod_group2) 


# do some checks:
pp_check(reef_accr_rat_mod_group2) #looks good
plot(reef_accr_rat_mod_group2, ask = FALSE) #looks good

#test hypotheses:
hypothesis(reef_accr_rat_mod_group2, c("Ratsyes+Ratsyes:Locationlagoon <0", #0.99 - should be ratty effect for lagoon
                                          "Ratsyes<0", #.98 should be ratty effect for fore-reef
                                          "Locationlagoon>0", #test for lagoon effect around non-ratty islands #.99
                                          "Locationlagoon+Ratsyes:Locationlagoon >0")) #test for lagoon effect (around ratty islands) #.96

#note - w/ corrected forereef values, all conclusions identical to original model, except stronger forereef effect of rats.

```


#try extracting estimates from combined model for reef accretion:
```{r}

reef_accr_rat_mod_group2 #not logged, so no need to transform...

##extract emmeans----

#full output for interaction effect:
reef_accr_rat_mod_group2%>%
emmeans(c("Location", "Rats"),
        type="response")%>%
      contrast("revpairwise") 
# contrast                                   estimate lower.HPD upper.HPD
# lagoon no - forereef shallow no               2.300     0.331    4.4051
# forereef shallow yes - forereef shallow no   -2.185    -4.161   -0.0934
# forereef shallow yes - lagoon no             -4.465    -6.472   -2.3803
# lagoon yes - forereef shallow no             -0.344    -2.351    1.7064
# lagoon yes - lagoon no                       -2.642    -4.695   -0.6511
# lagoon yes - forereef shallow yes             1.838    -0.135    3.9047


#full output for interaction effect (reversed order):
reef_accr_rat_mod_group2%>%
emmeans(c("Location", "Rats"),
        type="response")%>%
      contrast("pairwise")
# contrast                                   estimate lower.HPD upper.HPD
# forereef shallow no - lagoon no              -2.300   -4.4051    -0.331
# forereef shallow no - forereef shallow yes    2.185    0.0934     4.161
# forereef shallow no - lagoon yes              0.344   -1.7064     2.351
# lagoon no - forereef shallow yes              4.465    2.3803     6.472
# lagoon no - lagoon yes                        2.642    0.6511     4.695
# forereef shallow yes - lagoon yes            -1.838   -3.9047     0.135



###each group: 
reef_accr_rat_mod_group2%>%
emmeans("Rats", 
        by=c("Location"),
        type="response")
#Location = forereef shallow:
# Rats emmean lower.HPD upper.HPD
# no     3.58     0.545      6.30
# yes    1.42    -1.422      4.37

#Location = lagoon:
# Rats emmean lower.HPD upper.HPD
# no     5.92     2.929      8.75
# yes    3.27     0.341      6.13


#Point estimate displayed: median 
#HPD interval probability: 0.95 

#so that equals: 
3.58/1.42 #2.521127 times higher on forereef
5.92/3.27 #1.810398 times higher on lagoonal

```

#new - repeat with island/atoll to check if grouping structure affects conclusions----

#sediment---
```{r}
reef_sed_rat_mod_group_log2_isl<-
  brm(
 log_sed_delivery~Rats*Location +(1|Atoll/Island),
  data = reef_res_site_dat2, 
  iter = 3000, warmup = 1000, chains = 4, cores = 4,
   control = list(adapt_delta = 0.999, max_treedepth = 15), 
      file = "brms/reef_sed_rat_mod_group_log2_isl") 
print(reef_sed_rat_mod_group_log2_isl) # worked :)

pp_check(reef_sed_rat_mod_group_log2_isl) #looks good
plot(reef_sed_rat_mod_group_log2_isl, ask = FALSE)


#check estimates:
reef_sed_rat_mod_group_log2_isl.rg <- update(ref_grid(reef_sed_rat_mod_group_log2_isl), tran = "log") 

reef_sed_rat_mod_group_log2_isl.rg%>%
emmeans("Rats", 
        by=c("Location"),
        type="response")
#Location = forereef shallow:
# Rats response lower.HPD upper.HPD
# no     0.0633  2.62e-04     0.384
# yes    0.0292  3.56e-05     0.179

#Location = lagoon:
# Rats response lower.HPD upper.HPD
# no     0.1676  7.80e-04     1.024
# yes    0.0605  6.75e-05     0.360

#all identical point estimates, just wider HPDs


```

#reef accretion
```{r}
#can't log response because it goes below 0:

reef_accr_rat_mod_group2_isl<-
  brm(
 reef_accretion_2.0_mm_yr_corrected~Rats*Location + (1|Atoll/Island),
  data = reef_res_site_dat, 
  iter = 3000, warmup = 1000, chains = 4, cores = 4,
   control = list(adapt_delta = 0.999, max_treedepth = 15), 
      file = "brms/reef_accr_rat_mod_group2_isl") 
print(reef_accr_rat_mod_group2_isl) 


# do some checks:
pp_check(reef_accr_rat_mod_group2_isl) #looks good
plot(reef_accr_rat_mod_group2_isl, ask = FALSE) #looks good


reef_accr_rat_mod_group2_isl%>%
emmeans("Rats", 
        by=c("Location"),
        type="response")

#Location = forereef shallow:
# Rats emmean lower.HPD upper.HPD
# no     3.58  0.447563      6.52
# yes    1.41 -1.782715      4.35

#Location = lagoon:
# Rats emmean lower.HPD upper.HPD
# no     5.90  2.826334      9.03
# yes    3.27 -0.000458      6.17

#all really similar to og model. 

```


###-----plots for comparison: sediment-----
```{r}
draws_sed_atoll <-
  reef_sed_rat_mod_group_log2 %>%
  spread_draws(b_Ratsyes,
               `b_Locationlagoon`,
               `b_Ratsyes:Locationlagoon`) %>%
  mutate(model = "Atoll")

draws_sed_island <-
  reef_sed_rat_mod_group_log2_isl  %>%
  spread_draws(b_Ratsyes,
               `b_Locationlagoon`,
               `b_Ratsyes:Locationlagoon`)  %>%
  mutate(model = "Atoll/Island")

draws_sed_all <-
  bind_rows(draws_sed_atoll, draws_sed_island)%>%
  pivot_longer(
    cols = starts_with("b_"),
    names_to = "parameter",
    values_to = "value")%>%
    mutate(parameter = recode(parameter,
    "b_Ratsyes" = "Rat",
    "b_Locationlagoon" = "Lagoon",
    "b_Ratsyes:Locationlagoon" = "Rat x Lagoon"))%>%
    mutate(parameter = factor(parameter,
    levels = c("Rat",
               "Lagoon",
               "Rat x Lagoon")))

draws_sed_all


label_df <- draws_sed_all %>%
  distinct(parameter)

sed_comparison_plot<-
draws_sed_all %>%
  ggplot(aes(y = 0, x = value, fill = model, color = model)) +
  stat_slab(slab_alpha = .4, linewidth = .4) +
  facet_wrap(~parameter,
             scales = "free_x") +
  scale_fill_manual(values = c( "#5172B8", "#7294B2"))+
    scale_color_manual(values = c( "#5172B8", "#7294B2"))+
    xlab("Parameter estimate")+
 ylab("Posterior density")+
    geom_text(data = label_df, aes(x = -Inf, y = Inf, label = parameter), inherit.aes = FALSE, hjust = -0.15, vjust = 1.4, size = 3.5) +
  theme_bw()+
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
       # panel.border = element_blank(),
      #  legend.position = "none",
               legend.position=c(.9, .85),
        text = element_text(size = 10),
        axis.ticks.y = element_line(linewidth = .4, linetype = "solid", color = "black"),
        axis.line.y = element_line(linewidth = .4, linetype = "solid", color = "black"),
        axis.ticks.length=unit(.25, "cm"),
         strip.text = element_blank(),
        plot.margin = margin(t = 25,r = 5,b = 5,l = 15)) 

sed_comparison_plot

```



###-----plots for comparison: reef accretion-----
```{r}
draws_accr_atoll <-
  reef_accr_rat_mod_group2 %>%
  spread_draws(b_Ratsyes,
               `b_Locationlagoon`,
               `b_Ratsyes:Locationlagoon`) %>%
  mutate(model = "Atoll")

draws_accr_island <-
  reef_accr_rat_mod_group2_isl  %>%
  spread_draws(b_Ratsyes,
               `b_Locationlagoon`,
               `b_Ratsyes:Locationlagoon`)  %>%
  mutate(model = "Atoll/Island")

draws_accr_all <-
  bind_rows(draws_accr_atoll, draws_accr_island)%>%
  pivot_longer(
    cols = starts_with("b_"),
    names_to = "parameter",
    values_to = "value")%>%
    mutate(parameter = recode(parameter,
    "b_Ratsyes" = "Rat",
    "b_Locationlagoon" = "Lagoon",
    "b_Ratsyes:Locationlagoon" = "Rat x Lagoon"))%>%
    mutate(parameter = factor(parameter,
    levels = c("Rat",
               "Lagoon",
               "Rat x Lagoon")))

draws_accr_all


label_accr_df <- draws_accr_all %>%
  distinct(parameter)

accr_comparison_plot<-
draws_accr_all %>%
  ggplot(aes(y = 0, x = value, fill = model, color = model)) +
  stat_slab(slab_alpha = .5, linewidth = .4) +
  facet_wrap(~parameter,
             scales = "free_x") +
scale_fill_manual(values = c("#A14A4A", "#C28F8F"))+
  scale_color_manual(values = c("#A14A4A", "#C28F8F"))+
  xlab("Parameter estimate")+
 ylab("Posterior density")+
    geom_text(data = label_accr_df, aes(x = -Inf, y = Inf, label = parameter), inherit.aes = FALSE, hjust = -0.15, vjust = 1.4, size = 3.5) +
  theme_bw()+
  theme(panel.grid.major = element_blank(), # remove gridlines
        panel.grid.minor = element_blank(), #remove gridlines
        strip.background = element_blank(),
       # panel.border = element_blank(),
        legend.position=c(.9, .85),
        text = element_text(size = 10),
        axis.ticks.y = element_line(linewidth = .4, linetype = "solid", color = "black"),
        axis.line.y = element_line(linewidth = .4, linetype = "solid", color = "black"),
        axis.ticks.length=unit(.25, "cm"),
         strip.text = element_blank(),
        plot.margin = margin(t = 25,r = 5,b = 5,l = 15)) 

accr_comparison_plot


```


###combine plots and save-----
```{r}
accr_comparison_plot
sed_comparison_plot

Supp_Fig_groups<-plot_grid(accr_comparison_plot, sed_comparison_plot, labels = c("A Reef accretion potential", "B Sediment production potential"), label_fontface = "bold", nrow = 2,  hjust = 0)
Supp_Fig_groups

ggsave(Supp_Fig_groups, filename = "../figures/Supp_Fig_groups.jpg", width = 8.2, height = 8.2)
```

