---
title: "Fig2-3-4-root-length"
author: "CEB"
date: '2024-11-25'
output: html_document
---


#Terrestrial responses for figures 2-4: root productivity, biomass, length

#load packages
```{r}
library(tidyverse)

#for bayesian analysis:
library(brms)
library(tidybayes)

#for interpreting interactions:
library(emmeans)

#for plots:
library(ggnewscale)

```



#load data
```{r}
#data from eleanor:
root_dat<-read.csv("../data/RootData4Casey_021225.csv") #3.96 scaling factor for mg C to mj
root_dat

```


##Add Region column:
```{r}
root_dat<-
  root_dat%>%
  mutate(Region = case_when(grepl("SEY", Plot)~ "Seychelles",
                             TRUE~ "Tetiaroa"))%>%
  relocate(Region, .before = Motu)
root_dat

```


##Figure 2 - root production versus native forest (and soil n15) 

```{r}
##run model with Tetiaroa for main paper (because matches arthropods, and because have soil n15 data), also checked including Fregate and results don't change:

#split data, and center data----
tet_root_dat<-
root_dat%>%
  filter(Region == "Tetiaroa")%>%
    mutate(native_perc_c = base::scale(NativeForestFraction, center = TRUE, scale = FALSE),
         rootn15_c = base::scale(RootsN15, center = TRUE, scale = FALSE),
         soiln15_c = base::scale(SoilN15, center = TRUE, scale = FALSE))


##tetiaroa only (use soil n15 to match lizards/arthropods)----
tet_root_dat_log_c_mj_m2<-
  brm(
 log(NPP_MJ_m2_year) ~ native_perc_c * soiln15_c + (1|Motu), 
  data = tet_root_dat, 
  iter = 3000, warmup = 1000, chains = 4, cores = 4,
   control = list(adapt_delta = 0.999, max_treedepth = 15), 
      file = "brms/tet_root_dat_log_c_mj_m2") #worked fine

print(tet_root_dat_log_c_mj_m2)
pp_check(tet_root_dat_log_c_mj_m2) #looks good!!!
plot(tet_root_dat_log_c_mj_m2, ask = FALSE)

hypothesis(tet_root_dat_log_c_mj_m2, c("native_perc_c>0", #0.99
                                        "soiln15_c>0",#0.62
                                        "native_perc_c:soiln15_c>0")) #0.98

###extract effects (emmeans)-----
range(tet_root_dat$native_perc_c, na.rm=TRUE) #-23.40697  22.53837
mean(tet_root_dat$native_perc_c, na.rm=TRUE) #0
range(tet_root_dat$soiln15_c, na.rm=TRUE) #-4.913  5.367
mean(tet_root_dat$soiln15_c, na.rm=TRUE) #0
range(tet_root_dat$SoilN15, na.rm=TRUE) #9.09 19.37


#at 0, ~50, 100% native forest (min, mean, max), these are the effects of soil n15 on root npp in tetiaroa: ----
tet_root_dat_log_c_mj_m2%>%
emtrends(~native_perc_c, var = "soiln15_c", at = list(native_perc_c = c(-23.40697, 0, 22.53837))) #, type = "response", - need to tell emmeans log-transformed to get response to work: 
# native_perc_c soiln15_c.trend lower.HPD upper.HPD
#-23.4         -0.1664    -0.442     0.107
#  0.0          0.0297    -0.120     0.219
# 22.5          0.2337    -0.039     0.478



#back transform soil n15 effect for high native forest:----
exp(0.2337) #1.263265
exp(-0.039) #0.9617507
exp(0.478) #1.612845

#back transform soil n15 effect for low native forest:
exp(-0.1664) #0.8467075
exp(-0.442) #0.6427496
exp(0.107) #1.112934

1-exp(0.1664) #0.1810454 decrease
1-exp(-0.442) #0.3572504 decrease
exp(0.107)-1 #0.1129343 increase


#at min, mean, max soil n15 these are the effects of native forest on root npp in tetiaroa: -----
tet_root_dat_log_c_mj_m2%>%
emtrends(~soiln15_c, var = "native_perc_c", at = list(soiln15_c = c(-4.913, 0, 5.367))) #, type = "response", - need to tell emmeans log-transformed to get response to work: 
# soiln15_c native_perc_c.trend lower.HPD upper.HPD
#     -4.91           -0.000322  -0.05926    0.0530
#      0.00            0.042050   0.00881    0.0773
#      5.37            0.085417   0.03654    0.1505


#back transform native forest effect for high soil n15----
exp(0.085417) #1.089171
exp(0.03654) #1.037216
exp(0.1505) #1.162415

#back transform native forest effect for low soil n15:
exp(-0.000322) #0.9996781
exp(-0.05926) #0.9424617
exp(0.0530) #1.05443

1-exp(-0.000322) #0.0003219482 decrease - 0.03%
1-exp(-0.05926) #0.0575383 decrease - 5.8%
exp(0.0530)-1 #0.05442965 increase - 5.4%

```

#try to get relative effect sizes, using centered and scaled model for root npp versus native forest*soil n15------
```{r}
tet_root_dat_cs<-
tet_root_dat%>%
    mutate(native_perc_cs = base::scale(NativeForestFraction, center = TRUE, scale = TRUE),
         rootn15_cs = base::scale(RootsN15, center = TRUE, scale = TRUE),
         soiln15_cs = base::scale(SoilN15, center = TRUE, scale = TRUE))


##tetiaroa only (use soil n15 to match lizards/arthropods)----
tet_root_dat_log_cs_mj_m2<-
  brm(
 log(NPP_MJ_m2_year) ~ native_perc_cs * soiln15_cs + (1|Motu), 
  data = tet_root_dat_cs, 
  iter = 3000, warmup = 1000, chains = 4, cores = 4,
   control = list(adapt_delta = 0.999, max_treedepth = 15), 
      file = "brms/tet_root_dat_log_cs_mj_m2") #worked fine

print(tet_root_dat_log_cs_mj_m2)
pp_check(tet_root_dat_log_cs_mj_m2) #looks good!!!
plot(tet_root_dat_log_cs_mj_m2, ask = FALSE)

hypothesis(tet_root_dat_log_cs_mj_m2, c("native_perc_cs>0", #0.99
                                        "soiln15_cs>0",#0.62
                                        "native_perc_cs:soiln15_cs>0")) #0.98
#Hypothesis               Estimate      Est.Error       CI.Lower        CI.Upper    Evid.Ratio      Post.Prob Star
#(native_perc_cs) > 0	      0.60	      0.25	          0.19	          1.03	      74.47           	0.99	*
# > 0	                      0.12	      0.32          	-0.35	           0.67	       1.64	            0.62	
#(native_perc_cs:s... > 0	  0.44      	0.23          	0.08	            0.83	     43.44	          0.98	*

#so looks like native forest has largest relative effect (0.6), compared to interaction (0.44), and then soil (0.12). is this the correct interpretation?

```


##get sample sizes:
```{r}
tet_root_dat_cs
#n = 20 samples

tet_root_dat_cs%>%
  group_by(Motu)%>%
  summarize(count_sums = length(NPP_MJ_m2_year))
#4 measurements at each of 5 motu

```



#Figure 3: Root length ~ root productivity
```{r}
#Eleanor said likely something wrong with one core's biomass measurement - so remove (hit a coral or something):----
root_dat_no_out<-
  root_dat%>%
  filter(!(Motu == "Iti"&RootCore == 1))

root_dat_no_out_Tet<-
root_dat_no_out%>%
  filter(Region == "Tetiaroa")

##center variables-----------
root_dat_no_out_Tet_c<-
  root_dat_no_out_Tet%>%
   mutate(NPP_MJ_m2_year_c = base::scale(NPP_MJ_m2_year, center = TRUE, scale = FALSE))

root_length_prod_linear_Tetiaroa_no_c<-
  brm(
  Length_Km_m2~NPP_MJ_m2_year_c + (1|Motu),
  data = root_dat_no_out_Tet_c, 
  iter = 3000, warmup = 1000, chains = 4, cores = 4,
   control = list(adapt_delta = 0.999, max_treedepth = 15), 
      file = "brms/root_length_prod_linear_Tetiaroa_no_c") 

pp_check(root_length_prod_linear_Tetiaroa_no_c) #pretty good, not quite sampling true peak
plot(root_length_prod_linear_Tetiaroa_no_c, ask = FALSE)


print(root_length_prod_linear_Tetiaroa_no_c)

##extract estimates-----
hypothesis(root_length_prod_linear_Tetiaroa_no_c, "NPP_MJ_m2_year_c>0") #1

#extract effects----
root_length_prod_linear_Tetiaroa_no_c %>%
  spread_draws(b_NPP_MJ_m2_year_c) %>%
  median_hdi(b_NPP_MJ_m2_year_c)
#1.405793	1.153364	1.665224	
#each one unit increase in productivity associated with change in mean root length by 1.4 km/m2 (no transformations)

```



###FIGURE 4:--------
#bayesian models
```{r}

#log model looked best:
root_length_forest_cat_mod_log_no_out<-
  brm(
  log(Length_Km_m2)~NativeForestCover + (1|Motu),
  data = root_dat_no_out_Tet, 
  iter = 3000, warmup = 1000, chains = 4, cores = 4,
   control = list(adapt_delta = 0.999, max_treedepth = 15), 
      file = "brms/root_length_forest_cat_mod_log_no_out") 
print(root_length_forest_cat_mod_log_no_out) #worked

# do some checks:
pp_check(root_length_forest_cat_mod_log_no_out) #looks okay
plot(root_length_forest_cat_mod_log_no_out, ask = FALSE) #looks good
pp_check(root_length_forest_cat_mod_log_no_out, type = "boxplot") 
pp_check(root_length_forest_cat_mod_log_no_out, type = "violin_grouped", group = "NativeForestCover") 


hypothesis(root_length_forest_cat_mod_log_no_out, c("NativeForestCoverUnder75<0")) #0.96 posterior probability

```


#try extracting estimates for root length versus categorical native forest - log, no error
```{r}
root_length_forest_cat_mod_log_no_out
##extract emmeans----
root_length_forest_cat_mod_log_no_out.rg <- update(ref_grid(root_length_forest_cat_mod_log_no_out), tran = "log") #THIS LINE IS CLUTCH*** Now don't have to use link transformations, can use log response and still backtransform with emmeans


#full output for interaction effect:
root_length_forest_cat_mod_log_no_out.rg%>%
emmeans(c("NativeForestCover"),
        type="response")%>%
      contrast("pairwise") 
# contrast           ratio lower.HPD upper.HPD
# Over 75 / Under 75  4.58     0.019      20.7

#Point estimate displayed: median 
#Results are back-transformed from the log scale 
#HPD interval probability: 0.95 

#wide HPDIs, likely because not that many points.

root_length_forest_cat_mod_log_no_out.rg%>%
emmeans(c("NativeForestCover"),
        type="response")

root_length_forest_cat_mod_log_no_out.rg%>%
emmeans("NativeForestCover", 
        type="response")%>%
  contrast("trt.vs.ctrl")
# Under 75 / Over 75 0.218   0.00124     0.865


root_length_forest_cat_mod_log_no_out.rg%>%
emmeans("NativeForestCover", 
        type="response")
# NativeForestCover response lower.HPD upper.HPD
# Over 75              15.80     0.697     49.52
# Under 75              3.42     0.191      8.02



#get estimates as for other models (not emmeans)----
root_length_forest_cat_mod_log_no_out %>%
  spread_draws(b_NativeForestCoverUnder75) %>%
  median_hdi(exp(-b_NativeForestCoverUnder75)) #b_NativeForestCoverUnder75 
#matches estimates from above:
#4.580279	0.01404936	18.62117	0.95	median	hdi
#4.580279	19.15643083	20.91153	0.95	median	hdi

#not continuous interval, so repeat:
root_length_forest_cat_mod_log_no_out %>%
  spread_draws(b_NativeForestCoverUnder75) %>%
  median_hdci(exp(-b_NativeForestCoverUnder75))
#4.580279	0.01902669	20.65996	

```


#extract root length values for rats*vegetation:
```{r}


root_dat_no_out_Tet_rat%>%
  group_by(NativeForestCover, RatStatus)%>%
  summarize(median_length = median(Length_Km_m2),
            mean_length = mean(Length_Km_m2),
            n_length = length(Length_Km_m2),
            sd_length = sd(Length_Km_m2),
            sem_length = sd_length/sqrt(n_length))

```

